Supplementary Information

### 2020-08-14 doc/manuscript/MEE_manuscript.Rmd
Update MEE_manuscript.Rmd

**These results have important implications for using tree-rings to infer growth responses to slowly-changing environmental drivers, including climate, atmospheric CO~2~, and deposition of SO~2~ and NO~x~.** 
The observed trends in $\Delta r$ and $BAI$ with $DBH$ (Fig. 4) imply that two of the most commonly used growth-trend detection methods [@peters_detecting_2015] are inappropriate. 
Specifically, conservative detrending, which applies stiff splines or mathematical functions (e.g., negative exponential) to remove trends in $\Delta r$ before analyzing residuals, would not be reliable across the diversity of $\Delta r$-$DBH$ relationships observed here, and also has a tendency to remove known long-term trends [@peters_detecting_2015].
Basal area correction -- i.e., assuming that $BAI$ is fundamentally independent of tree size after the removal of the juvenile growth phase--is also problematic because $BAI$ shows a variety of trends with $DBH$ across large size classes. The most common pattern--*a decrease with $DBH$ after peaking at intermediat sizes*--would imply that the basal area correction is most commonly biased towards finding negative trends, consistent with the results of the literature review of @peters_detecting_2015.
Alternative methods, such as regional curve standardization [e.g., REF] and size class isolation [e.g., @van_der_sleen_no_2015], are compatible with the size trends observed here and consistent with the recommendations of @peters_detecting_2015.

>>>>

**These results have important implications for using tree-rings to infer growth responses to slowly-changing environmental drivers, including climate, atmospheric CO~2~, and deposition of SO~2~ and NO~x~.** 
The observed trends in $\Delta r$ and $BAI$ with $DBH$ (Fig. 4) imply that two of the most commonly used growth-trend detection methods [@peters_detecting_2015] are inappropriate. 
Specifically, conservative detrending, which applies stiff splines or mathematical functions (e.g., negative exponential) to remove trends in $\Delta r$ before analyzing residuals, would not be reliable across the diversity of $\Delta r$-$DBH$ relationships observed here, and also has a tendency to remove known long-term trends [@peters_detecting_2015].
Basal area correction -- i.e., assuming that $BAI$ is fundamentally independent of tree size after the removal of the juvenile growth phase--is also problematic because $BAI$ shows a variety of trends with $DBH$ across large size classes. The most common pattern--*a decrease with $DBH$ after peaking at intermediate sizes*--would imply that the basal area correction is most commonly biased towards finding negative trends, consistent with the results of the literature review of @peters_detecting_2015.
Alternative methods, such as regional curve standardization [e.g., REF] and size class isolation [e.g., @van_der_sleen_no_2015], are compatible with the size trends observed here and consistent with the recommendations of @peters_detecting_2015.
